The pollination trade-off

### 2018-08-24 paper/manuscript.Rmd
Add figures results models quantity and quality
Close #16

```{r fig-model-results-global, fig.height = 2, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain. Results are shown for models with explanatory var"}
drake::readd(fig_model_results_global)
```

The gain in conspecific pollen is positively correlated with the gain in heterospecific pollen. 
The slope of the relationship is such that it is more likely that the gain on heterospecific pollen increases faster than the gain on conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)A). 
In addition, we found that from all the explanatory variables examined, only the plant's relative abbundance has a positive effect on the proportion of conspecific pollen gained (Figure \@ref(fig:fig-trade-off-predictions)B). 
For most of the parameter space plants obtain a larger proportion of heteropspecific than conspecific pollen. 
However, plants can obtain a larger proportion of conspecific pollen when they have high abundance and to a smaller extent when they have a low degree. 
When examining the extent of facilitation at the species level, we found that XXX (Figure \@ref(fig:fig-trade-off-predictions)B).

>>>>

```{r fig-model-results-global, fig.height = 1.5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain. Results are shown for models with explanatory var"}
drake::readd(fig_coefficient_averages)
```

```{r fig-average-qual-quant, fig.height=2, fig.width=3.5, fig.cap="asd"}
drake::readd(fig_average_qual_quant)
```
The gain in conspecific pollen is positively correlated with the gain in heterospecific pollen. 
The slope of the relationship is such that it is more likely that the gain on heterospecific pollen increases faster than the gain on conspecific pollen (Figure \@ref(fig:fig-trade-off-predictions)A). 
In addition, we found that from all the explanatory variables examined, only the plant's relative abbundance has a positive effect on the proportion of conspecific pollen gained (Figure \@ref(fig:fig-trade-off-predictions)B). 
For most of the parameter space plants obtain a larger proportion of heteropspecific than conspecific pollen. 
However, plants can obtain a larger proportion of conspecific pollen when they have high abundance and to a smaller extent when they have a low degree. 
When examining the extent of facilitation at the species level, we found that XXX (Figure \@ref(fig:fig-trade-off-predictions)B).

### 2018-08-24 paper/supp-info.Rmd
Add figures results models quantity and quality
Close #16

```{r table-variable-importance, results='asis'}
drake::loadd(model_formula_ranking)

@@

model_weights <- model_formula_ranking$by_model_set %>%
  dplyr::filter(scale == "community") %>%
  dplyr::group_by(pollen_category) %>%
  dplyr::mutate(likelyhood = get_likelyhoods(delta_AIC_median), 
                weight = get_weights(likelyhood))

crosses <- purrr::cross2(terms, c("conspecific", "heterospecific"))
crosses %>%
  purrr::map(~model_weights$weight[stringr::str_detect(model_weights$fixed_formula, .[[1]]) & model_weights$pollen_category == .[[2]]]) %>%
  purrr::map(sum) %>%
  purrr::map2_df(crosses, 
              ~ dplyr::data_frame(
                var = .y[[1]],
                pollen_category = .y[[2]], 
                importance = .x)
              ) %>%
  dplyr::mutate(importance = round(importance, digits = 3)) %>%
  dplyr::rename(term = var) %>%
  humanize() %>%
  tidyr::spread(pollen_category, importance) %>%
  dplyr::arrange(dplyr::desc(conspecific), heterospecific) %>%
  dplyr::rename(`fixed effect`= term, 
                `conspecific pollen` = conspecific, 
                `heterospecific pollen` = heterospecific) %>%
  knitr::kable(caption = "Relative variable impotance of the four vaariables included as fixed effects. Variable importance was calculated as the sum of the median Akaike weights (Table \\ref{tab:table-aic-fixed-models}) of each candidate model set that includes the variable.", 
               booktabs = TRUE) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::add_header_above(c(" ", "variable importance" = 2))
```

```{r fig-model-results, fig.height = 3.5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain. Only results for the models with the most parsimonous fixed effects. "}
drake::readd(fig_all_model_results)
```

>>>>

```{r table-variable-importance, results='asis'}
drake::loadd(model_formula_ranking)
```{r fig-model-results, fig.height = 3.5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain. Only results for the models with the most parsimonous fixed effects. "}
drake::readd(fig_all_model_results)
```

@@

model_weights <- model_formula_ranking$by_model_set %>%
  dplyr::group_by(pollen_category) %>%
  dplyr::mutate(likelyhood = get_likelyhoods(delta_AIC_median), 
                weight = get_weights(likelyhood))

crosses <- purrr::cross2(terms, c("conspecific", "heterospecific"))
crosses %>%
  purrr::map(~model_weights$weight[stringr::str_detect(model_weights$fixed_formula, .[[1]]) & model_weights$pollen_category == .[[2]]]) %>%
  purrr::map(sum) %>%
  purrr::map2_df(crosses, 
              ~ dplyr::data_frame(
                var = .y[[1]],
                pollen_category = .y[[2]], 
                importance = .x)
              ) %>%
  dplyr::mutate(importance = round(importance, digits = 3)) %>%
  dplyr::rename(term = var) %>%
  humanize() %>%
  tidyr::spread(pollen_category, importance) %>%
  dplyr::arrange(dplyr::desc(conspecific), heterospecific) %>%
  dplyr::rename(`fixed effect`= term, 
                `conspecific pollen` = conspecific, 
                `heterospecific pollen` = heterospecific) %>%
  knitr::kable(caption = "Relative variable impotance of the four vaariables included as fixed effects. Variable importance was calculated as the sum of the median Akaike weights (Table \\ref{tab:table-aic-fixed-models}) of each candidate model set that includes the variable.", 
               booktabs = TRUE) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::add_header_above(c(" ", "variable importance" = 2))
```
```{r fig_effect_quant_qual, fig.height=3.5, fig.cap="asd"}
drake::loadd(fig_effect_quant_qual)

```{r fig-model-results, fig.height = 3.5, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain. Only results for the models with the most parsimonous fixed effects. "}
drake::readd(fig_all_model_results)
cowplot::plot_grid(
 fig_effect_quant_qual[[1]], 
 fig_effect_quant_qual[[2]],
  labels = LETTERS[1:2], 
  label_size = 8, ncol = 2)
```
